\documentclass[a4paper, 10pt]{article}
\usepackage{/run/media/mamnoonsiam/Programming/GitLab/general-writings/style}

\title{Graph Theory, Class 1}
\author{Mamnoon Siam}
\date{\today}

\begin{document}
  \maketitle
  \section{Definitions and Notations}
  \begin{definition}[Degree]
    Given a vertex $v$, the \textbf{degree} of $v$ is defined to be the
    number of edges containing $v$ as an endpoint.
  \end{definition}
  \begin{definition}[Complement Graph]
    Let $G=(V, E)$ be a graph. The \textbf{complement} $\bar{G}$ of $G$ is a
    graph with the same vertex set as $G$ and $E(\bar{G})=\{e \notin E(G)\}$.
    i.e. $\bar{G}$ has edges exactly where there are no edges in $G$.
  \end{definition}
  \begin{definition}
    Let $G$ be a connected graph. Then $G$ contains a subgraph which is a
    tree containing all the vertices of $G$. Such a subgraph is called
    \textbf{spanning tree} of $G$.
  \end{definition}
  \begin{itemize}
    \item Sometimes its easier to solve some problem if you consider some
      spanning tree of the given graph because trees are easier to deal with.
    \item Some of the most occurred spanning trees are dfs and bfs trees
      (both have theirs own perks).
  \end{itemize}
  \begin{definition}[Tournament Graphs]
    A directed graph $G(V, E)$ is called tournament \textit{iff} for every
    pair $(a,b) \, | \, 1 \le a < b \le |V|$, there exists either a directed
    edge from $a$ to $b$ or a directed edge from $b$ to $a$. In other words,
    A tournament is defined to be a complete directed graph.
  \end{definition}
  \begin{definition}[Hamiltonian Path]
    A path that visits every vertex \textbf{exactly} once.
  \end{definition}
  \begin{definition}[Hamiltonian Cycle]
    A Cycle that visits every vertex \textbf{exactly} once.
  \end{definition}
  \section{Notations}
  \begin{enumerate}
    \item Maximum degree of any node in graph $G$ is denoted with $\Delta(G)$.
  \end{enumerate}
  \section{Problems}
  \subsection{Basic Stuff}
  \begin{problem}
    \label{degree-sum}
    Let $G$ be a graph with $n$ vertices, $m$ edges and the degrees of the
    $n$ vertices are $d_{1}, d_{2}, \cdots, d_{n}$ Prove that
    \[
      \sum_{i=1}^{n} d_{i}=2 m
    .\]
  \end{problem}
  \begin{problem}
    Let $G$ be a disconnected graph. Prove that its complement $\bar{G}$ is
    connected.
  \end{problem}
  \begin{problem}
    Prove that a graph is bipartite if and only if it does not contain an odd
    cycle.
  \end{problem}
  \begin{problem}
    Characterize graphs with $n$ vertices and $n$ edges (connected or
    disconnected).
  \end{problem}
  \begin{problem}
    Characterize graphs with $\Delta(G) \le 2$.
  \end{problem}

  \subsection{Induction}
  \begin{problem}
    Given an undirected connected graph $G(V, E)$, find a subset $S$ of $E$,
    such that in the graph $G^\prime(V, S)$, every node has odd degree. Also,
    find a condition necessary and sufficient condition for this subset to
    exist.
  \end{problem}
  \begin{problem}
    Prove that every tournament graph has a Hamiltonian path.
  \end{problem}
  \begin{problem}[\href{https://codeforces.com/problemset/problem/%
    1019/C}{Sergey's Problem}]
    Prove that, for every directed graph $G(V, E)$ without self-loop, there
    exists $Q \subseteq V$, such that there is no directed edge between two
    vertices from $Q$ and every vertex not belonging to $Q$ can be reached
    from a vertex $\in Q$ in at most two moves.
  \end{problem}

  \subsection{Coloring}
  \begin{problem}
    For a $n \times m$ grid, find necessary and sufficient condition for is
    to have a Hamiltonian Cycle. (you can move from one cell to another
    \textit{iff} they share a side)
  \end{problem}
\end{document}
